---
title: "About this blog"
description: |
  This Blog is continuously maintained by Saldae Analytics & Services
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Saldae Analytics 
We are an innovative and value driven start up preaching for Advanced Analytics solutions and consists of a  **web based platform** enabling a handy and insightful data exploration, analysis and fully automatized forecasting tool for  price, demand, production, sales prediction...<br>
Our product is mainly designed for companies heading in the direction of data-driven business transformation.<br>

For more details, please feel free to visit our website and get in touch with us : <br>

<p style="color:green;">https://www.saldaeanalytics.com/</p>



```{r rShiny, , class="blue-outline", out.width= "130%"}
shiny_img_path <- "images/Saldae_about.png"
knitr::include_graphics(shiny_img_path)

```


<!-- ## Contributors -->

<!-- ### Farid Azouaou -->

<!-- :::: {style="display: flex;"} -->

<!-- ::: {.column width="25%" data-latex="{0.05\textwidth}"} -->

<!-- ```{r, echo = FALSE,out.width = "80%"} -->
<!-- farid_img_path <- "images/farid_azouaou.jpg" -->
<!-- knitr::include_graphics(farid_img_path) -->

<!-- ``` -->

<!-- ::: -->

<!-- :::  {.column width="70%" data-latex="{0.4\textwidth}"} -->
<!-- - **Senior Data Scientist** : I am Data Passionate, no matter which problematic in front of me, the only condition, there is data to handle. -->

<!-- - Msc Industrial Mathematics  Hamburg University - Germany- -->
<!-- - Msc Applied Mathematics Operations Research - Bejaia University- Algeria -->
<!-- ::: -->
<!-- :::: -->

<!-- ### Assirem Loualia -->

<!-- :::: {style="display: flex;"} -->

<!-- ::: {.column width="25%" data-latex="{0.05\textwidth}"} -->

<!-- ```{r, , class = "blue-outline",out.width = "80%"} -->
<!-- farid_img_path <- "images/assirem_loualia.jpg" -->
<!-- knitr::include_graphics(farid_img_path) -->

<!-- ``` -->

<!-- ::: -->

<!-- :::  {.column width="70%" data-latex="{0.4\textwidth}"} -->
<!-- - **Senior IT Architect** : -->

<!-- - Msc Computer Science  Pierre et Marie Curie University - Paris France- -->
<!-- - Msc Computer Science major: Networks - Bejaia University- Algeria -->
<!-- ::: -->
<!-- :::: -->