---
title: "End-to-End R-based prod Analytics projects(Part 2)"
description: |
  A short journey through most useful R features and good practices to make successful productive Machine Learning projects.
preview: images/R-dashboard.PNG
author:
  - name: Saldae Analytics
    url: https://www.saldaeanalytics.com/
    email: contact@saldaeanalytics.com
date: 10-13-2020
categories:
  - MLops
  - Data Science
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    self_contained: false
    css: end_to_end_background.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Analytics

### Econometrics 

- **forecast**
- **prophet**

### Machine Learning Suit: tidymodels
If *shallow learning* does not work then use *deep learning* , if else then *blame your data*


#### Unsupervised Learning



#### Supervised Learning

**Classification**


**Regression**



#### Reinforcement Learning



### Save your results : data , model

* **saveRDS**
* **feather**

## Smart Dashboarding and Reporting 

### Shiny


Shiny has proved itself a great tool for communicating data science teams’ results. However, developing a Shiny app for a large scope project that will be used commercially by more than dozens of users is not easy.

The first challenge is User Interface (UI): the expectations are that the app should not vary from modern web pages.

Secondly, performance directly impacts user experience (UX), and it’s difficult to maintain efficiency with growing requirements and user base.


```{r rShiny, , class="blue-outline", out.width= "110%"}
shiny_img_path <- "images/R-shiny.PNG"
knitr::include_graphics(shiny_img_path)

```


### rmarkdown 

- **flexdashboard**


```{r flexdashboard, , class="blue-outline", out.width= "110%", paged.print=TRUE}
farid_img_path <- "images/R-dashboard.PNG"
knitr::include_graphics(farid_img_path)

```

- **pretty_doc**

